Decomposition-based Job-shop Scheduling with Constrained Clustering

### 2021-10-14 Artificial Intelligence and Machine Learning/PADL_conference/Paper_draft_v1.tex

\section{Feature Extraction}
\label{sec:features}
Application of machine learning methods to scheduling problems requires careful selection of data describing the hidden dependencies between operations of different jobs \cite{ismail2012production,nasiri2019data}. Clustering methods, which we aim to apply in our approach, are not an exception. Thus, a clustering method requires an informative set of features describing jobs, their operations, and machines of an instance to find patterns resulting in a beneficial decomposition of all operations in time windows.

>>>>

\section{Feature Extraction}
\label{sec:features}
The application of machine learning methods to scheduling problems requires a careful selection of data describing the hidden dependencies between operations of different jobs \cite{ismail2012production,nasiri2019data}. Clustering methods, which we intend to apply in our approach, are not an exception to this. That is, a clustering method requires an informative set of features characterizing the jobs, their operations, and machines of a problem instance to identify patterns resulting in a beneficial decomposition of the operations into time windows.
